Final assignment presentation

### 2022-12-01 summary_final_assingment.Rmd
Update summary_final_assingment.Rmd

```{r }
dfmat <- corp %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  tokens_replace(pattern = lexicon::hash_lemmas$token, replacement = lexicon::hash_lemmas$lemma) %>%
  tokens_wordstem() %>%
  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "use", "author","fund","provid","program","requir","divis","titl","appropri","specifi")) %>%
  dfm()

@@

dfmatCon <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp$session) %>%dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm_trim(min_termfreq = 3)

@@

#Wordcloud congress 115
```

@@

dfmat_115 <- dfm_subset(dfmat, session == 115)
corp_115 <- df %>% filter(session == 115) %>% rename(text = summary) %>% corpus()
modelpart15 <- dfm(corp_115, remove = stopwords("english"),remove_numbers = TRUE, remove_punct = TRUE, groups = corp_115$party) %>%
   dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm_trim(min_termfreq = 3)

@@

corp_116 <- df %>% filter(session == 116) %>% rename(text = summary) %>% corpus()
modelpart16 <- dfm(corp_116, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp_116$party) %>% dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used")) %>%
  dfm_trim(min_termfreq = 3)

>>>>

```{r }
dfmat <- corp %>%
  tokens(remove_punct = TRUE, remove_numbers = TRUE, remove_symbols = TRUE) %>%
  tokens_remove(patter = stopwords("en")) %>%
  tokens_replace(pattern = lexicon::hash_lemmas$token, replacement = lexicon::hash_lemmas$lemma) %>%
  tokens_wordstem() %>%
  tokens_remove(c("sec","bill","act", "section", "funds", "shall","must", "used","provided","title","program","author","fund","provid","program","requir","divis","titl","appropri","specifi","prohibits", "also","congress","provides","appropriations","designates")) %>%
  dfm()

@@

dfmatCon <- dfm(corp, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp$session) %>%dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used","provided","title","program","author","fund","provid","program","requir","divis","titl","appropri","specifi","prohibits", "also","congress","provides","appropriations","designates")) %>%
  dfm_trim(min_termfreq = 3)

@@

@@

dfmat_115 <- dfm_subset(dfmat, session == 115)
corp_115 <- df %>% filter(session == 115) %>% rename(text = summary) %>% corpus()
modelpart15 <- dfm(corp_115, remove = stopwords("english"),remove_numbers = TRUE, remove_punct = TRUE, groups = corp_115$party) %>%
   dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used","provided","title","program","author","fund","provid","program","requir","divis","titl","appropri","specifi","prohibits", "also","congress","provides","appropriations","designates")) %>%
  dfm_trim(min_termfreq = 3)

@@

corp_116 <- df %>% filter(session == 116) %>% rename(text = summary) %>% corpus()
modelpart16 <- dfm(corp_116, remove = stopwords("english"), remove_numbers = TRUE, remove_punct = TRUE, groups = corp_116$party) %>% dfm_remove(c("sec","bill","act", "section", "funds", "shall","must", "used","provided","title","program","author","fund","provid","program","requir","divis","titl","appropri","specifi","prohibits", "also","congress","provides","appropriations","designates")) %>%
  dfm_trim(min_termfreq = 3)
